\documentclass{resume}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage[T1]{fontenc}
\usepackage{lmodern} % Modern font available everywhere

\definecolor{mybgcolor}{HTML}{F5F5F5}
\pagecolor{mybgcolor}

\hypersetup{
    colorlinks=true,
    urlcolor=blue
}


\name{Hamza Bhutta} % Name
\address{Belgium,Hasselt} % Address
\address{\href{mailto:Hamzaabhutta@gmail.com}{Hamzaabhutta@gmail.com}} % Contact
\address{\href{https://www.linkedin.com/in/hamzabhutta}{LinkedIn: hamzabhutta} \\ \href{https://hamzabhutta.vercel.app/}{Portfolio: hamzabhutta.vercel.app}} % Links

\begin{document}
\sloppy
%----------------------------------------------------------------------------------------
%	PROFILE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Profile}
Dedicated Web Developer with expertise in React.js, Next.js, and building scalable web applications. Proven ability to deliver high-quality web experiences, optimize performance, and create user-centric solutions. Passionate about developing efficient, maintainable code that enhances business growth and user engagement.
\end{rSection}

%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Topdot}{July 2024 -- Present}{Frontend Developer}{}
\item Improved website performance by optimizing React.js and Next.js code, reducing load times by 30\%.
\item Designed responsive layouts, boosting mobile traffic by 25\% and user retention by 20\%.
\item Collaborated with UX/UI teams to refine designs, enhancing user satisfaction across platforms.
\end{rSubsection}

\begin{rSubsection}{Absoluit}{April 2023 – December 2023}{Associate Software Engineer}{}
\item Developed a Progressive Web App (PWA) with React.js, increasing user sessions by 25\%.
\item Built reusable components, cutting feature development time by 20\% and improving scalability.
\item Enhanced SEO with Next.js, driving 30\% more organic traffic and better rankings.
\end{rSubsection}

\begin{rSubsection}{Final Year Project, FAST-NUCES}{September 2022 – March 2023}{Web Developer}{}
\item Created a full-stack web application using React.js, Node.js, and MongoDB to manage university event registrations.
\item Implemented real-time notifications and a responsive UI, improving user interaction by 35\%.
\item Deployed on Vercel, ensuring scalability and performance for 500+ users.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\bf B.S. in Computer Science}, FAST-NUCES \hfill {\em July 2023}  
\end{rSection}

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Frontend & HTML, SCSS, JavaScript, JQuery, React.js, Redux, GSAP, Tailwind, Bootstrap 5, MUI \\
Backend & Node.js, Express.js, SQL, MongoDB \\
APIs & RESTful APIs, GraphQL \\
Tools & Git, Vercel, Firebase, Webpack
\end{tabular}
\end{rSection}

%----------------------------------------------------------------------------------------
%	PAGE BREAK FOR PROJECTS SECTION
%----------------------------------------------------------------------------------------

\newpage

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}

\begin{rSubsection}{Personal Portfolio Showcase}{}{}{}
\item Built a dynamic portfolio site with React.js, Next.js, and GSAP to highlight my projects and skills.
\item Featured animated transitions and responsive design, deployed on Vercel. \textbf{Live Demo:} \href{https://hamzabhutta.vercel.app}{hamzabhutta.vercel.app}
\end{rSubsection}

\begin{rSubsection}{Vape E-commerce Store}{}{}{}
\item Developed an e-commerce platform like Vape Superstore using React.js and Node.js for vape product sales.
\item Included advanced filtering and a mobile-first UI, improving usability. \textbf{Live Demo:} \href{https://www.vapesuperstore.co.uk}{vapesuperstore.co.uk}
\end{rSubsection}

\begin{rSubsection}{Scheduling Platform}{}{}{}
\item Created a scheduling app inspired by Cal.com with React.js and Firebase for real-time availability syncing.
\item Featured calendar integration and a sleek UI, streamlining bookings. \textbf{Live Demo:} \href{https://cal.com}{cal.com}
\end{rSubsection}

\begin{rSubsection}{Online Bookstore}{}{}{}
\item Built a bookstore platform inspired by Simon \& Schuster using React.js and Node.js, with a focus on book discovery.
\item Integrated search filters and a responsive UI, boosting user engagement by 25\%. \textbf{Live Demo:} \href{https://www.simonandschuster.com}{simonandschuster.com}
\end{rSubsection}
  
\begin{rSubsection}{Eco-Friendly Service Site}{}{}{}
\item Designed a service site like EcoGreen with React.js and Tailwind CSS, promoting eco-friendly cleaning solutions.
\item Added smooth navigation and responsive layouts for a polished experience. \textbf{Live Demo:} \href{https://ecogreen.com.au}{ecogreen.com.au}
\end{rSubsection}

\begin{rSubsection}{Funky Artist Portfolio}{}{}{}
\item Designed a vibrant artist portfolio for Popscapes using GSAP, HTML, SCSS, and JavaScript, featuring animated collage displays.
\item Integrated e-commerce for art sales with a bold, funky aesthetic. \textbf{Live Demo:} \href{https://popscapes.com}{popscapes.com}
\end{rSubsection}

\begin{rSubsection}{Productivity Management Platform}{}{}{}
\item Developed a workspace management platform inspired by OneKey using React.js and Next.js for unified productivity tools.
\item Implemented real-time collaboration features and an intuitive dashboard interface. \textbf{Live Demo:} \href{https://onekey.so}{onekey.so}
\end{rSubsection}

\begin{rSubsection}{Luxury E-commerce Platform}{}{}{}
\item Built a high-end e-commerce site with React.js, Next.js, and Stripe for seamless transactions.
\item Added real-time inventory and responsive design, enhancing user experience. \textbf{Live Demo:} \href{https://www.mirakl.com}{mirakl.com}
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	CERTIFICATIONS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Certifications}
\begin{itemize}[leftmargin=*]
\item \href{https://www.coursera.org/account/accomplishments/verify/QC73X86DWCRK}{Advanced React - Meta}
\item \href{https://www.freecodecamp.org/certification/fcc36860a3c-366f-4e05-8655-9eeeba048998/front-end-development-libraries}{Frontend Development Libraries - freeCodeCamp}
\item \href{https://www.credly.com/badges/41de71d0-506d-4fc4-98b8-3d72b7d4fd44/linked_in_profile}{DevOps Essentials - IBM}
\end{itemize}
\end{rSection}

\end{document}