\documentclass[10pt]{article}

% Configuring page geometry for maximum space utilization
\usepackage[left=0.5in,top=0.4in,right=0.5in,bottom=0.4in]{geometry}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage[T1]{fontenc}
\usepackage[sfdefault]{roboto}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{fontawesome5}

% Compact font sizes for single page
\newcommand{\sectionfontsize}{\large}
\newcommand{\headerfontsize}{\Large}
\newcommand{\bodyfontsize}{\small}

% Remove section numbering
\setcounter{secnumdepth}{0}

% Professional color scheme
\definecolor{mybgcolor}{HTML}{FFFFFF}
\definecolor{headercolor}{HTML}{2d3748}
\definecolor{linkcolor}{HTML}{2563eb}
\pagecolor{mybgcolor}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    urlcolor=linkcolor,
    linkcolor=linkcolor
}

% Compact section formatting
\titleformat{\section}{\sectionfontsize\bfseries\color{headercolor}}{\thesection}{1em}{}[\titlerule]
\titlespacing*{\section}{0pt}{8pt}{3pt}

% Compact header
\newcommand{\resumeHeader}[1]{
    \begin{center}
        {\headerfontsize\bfseries\color{headercolor} Hamza Bhutta} \\[2pt]
        {\normalsize\color{headercolor} Digital \& Data Specialist} \\[4pt]
        {\bodyfontsize\color{headercolor}
            \faPhone~ +92 311 1208388 \quad
            \faEnvelope~\href{mailto:hamzaabhutta@gmail.com}{hamzaabhutta@gmail.com} \quad
            \faLinkedin~\href{https://www.linkedin.com/in/hamzabhutta}{linkedin.com/in/hamzabhutta} \quad
            \faGlobe~\href{https://hamzabhutta.vercel.app/}{hamzabhutta.vercel.app}
        } \\[3pt]
        {\bodyfontsize\color{headercolor} Lahore, Pakistan | Open to Remote Roles | Blue Card Eligible}
        \vspace{6pt}
    \end{center}
}

% Compact itemize
\setlist[itemize]{leftmargin=15pt,itemsep=0.1em,topsep=0.1em,font=\bodyfontsize,parsep=0pt}

\begin{document}
\pagestyle{empty}

% Remove paragraph indentation globally
\setlength{\parindent}{0pt}

% Header
\resumeHeader{}

% Professional Summary
\section{Professional Summary}
\bodyfontsize
Digital and Data Specialist with 2+ years of experience delivering technology solutions in complex organisations. Skilled at bridging technical and non-technical teams, simplifying complex concepts for diverse audiences, and supporting digital transformation projects. Strong background in web systems, data-driven applications, and process optimisation, with proven ability to work across cultures in remote, global teams.

%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section{Professional Experience}

\textbf{Software Frontend Developer} | Topdot \hfill July 2024 -- Present
\begin{itemize}
\item Contributed to digital reform by modernising online services through interactive applications.
\item Improved performance and accessibility, achieving 90\%+ Lighthouse scores in alignment with digital standards.
\item Shared knowledge of modern tools and practices across teams, building capacity in digital delivery.
\end{itemize}

\textbf{Associate Software Engineer} | Absoluit \hfill April 2023 – December 2023
\begin{itemize}
\item Supported digital transformation initiatives by migrating legacy systems into scalable React.js platforms.
\item Acted as liaison between technical teams and business stakeholders, ensuring delivery matched policy requirements.
\item Delivered structured outputs through agile processes, Jira workflows, and transparent reporting.
\end{itemize}

%----------------------------------------------------------------------------------------
%	DIGITAL & DATA SKILLS
%----------------------------------------------------------------------------------------
\section{Digital \& Data Skills}
\begin{tabularx}{\textwidth}{@{} l X @{}}
\textbf{Digital Transformation:} & System modernisation, process optimisation, automation with AI tools \\
\textbf{Data:} & Building dashboards, APIs for data exchange, supporting governance through structured delivery \\
\textbf{Collaboration:} & Stakeholder communication, cross-cultural teamwork, knowledge sharing \\
\textbf{Governance:} & Agile delivery, version control, documentation, alignment with organisational policies \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------
\section{Selected Projects}

\textbf{Open Data E-Commerce Platform} \\
\textit{React.js, Node.js, MongoDB, Stripe API}
\begin{itemize}
\item Designed a data-driven platform with real-time reporting, secure transactions, and admin dashboards.
\item Applied governance principles in handling user data, with secure authentication and access control.
\end{itemize}

\textbf{Task Management Dashboard} \\
\textit{Vue.js, Node.js, PostgreSQL}
\begin{itemize}
\item Supported digital workflow reform through collaborative dashboards with progress analytics.
\item Built features to enable transparency in tasks, document sharing, and stakeholder alignment.
\end{itemize}

%----------------------------------------------------------------------------------------
%	EDUCATION & CERTIFICATIONS
%----------------------------------------------------------------------------------------
\section{Education \& Certifications}
\textbf{Bachelor of Science in Computer Science} | FAST-NUCES \hfill 2023 \\[2pt]
\textbf{Certifications:} Advanced React (Meta/Coursera), Frontend Development Libraries (freeCodeCamp), DevOps Essentials (IBM)

%----------------------------------------------------------------------------------------
%	KEY STRENGTHS
%----------------------------------------------------------------------------------------
\section{Key Strengths}
\begin{itemize}
\item \textbf{Communication:} Able to explain technical concepts clearly to policy and non-technical audiences.
\item \textbf{Cross-cultural collaboration:} Experience working in diverse, remote-first teams across countries.
\item \textbf{Knowledge sharing:} Actively contributed documentation, training, and open-source projects.
\item \textbf{Adaptability:} Comfortable working in evolving digital and policy environments.
\end{itemize}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------
\section{Additional Information}
\textbf{Languages:} English (Professional), Urdu (Native) \quad \textbf{Experience:} 2+ years \quad \textbf{Availability:} 1 week \\ 
\textbf{Open Source:} Contributor to React ecosystem \quad \textbf{Interests:} Digital Governance, Open Data, Public Sector Reform

\end{document}
